### 2024-06-17 conteudo/tool/architecture.tex
complete initial version of architecture, 17/06

\begin{itemize}
	\begin{item}
		\textbf{C}:
	\end{item}
	\begin{item}
		\textbf{Java}:
	\end{item}
\end{itemize}

>>>>

\begin{itemize}
	\begin{item}
		\textbf{C}: Given a source code file, we extract every code block from it, maintaining the depth of the code block in
		the code context and som lines of code before the definition of the code block. By the C programming language's grammar, 
		the functions are defined in a global context, with depth of 0. There are other elements with the same depth as functions,
		we differentiate them by analysing if the first non-empty character before the curly brackets of the code block is a close 
		parenthesis, since functions are the only elements that respect this pattern in the C programming language.
	\end{item}
	\begin{item}
		\textbf{Java}: Given a source code file, we extract every code block from it, maintaining the depth of the code block in
		the code context and som lines of code before the definition of the code block. By the Java's grammar, 
		the functions are defined inside classes. There are different depths which we can have functions, as Java accepts inner
		classes. We differentiate functions of other elements by analysing if the first non-empty character before the curly brackets of the code block is a close 
		parenthesis, since there are others elements which also respect this pattern such as for loop, we would need to apply other 
		filters. We chose to only analyse functions of depth 1, which ignores every others elements that respect the previously
		filters, but as counterpart, functions declared inside Inner Classes are not supported by our extractor. We made this choice
		as there are not inner classes on the codebases explored in this work.
